---
title: "Analysis of fake data"
author: "Brian Barkley"
date: "4/2/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include=FALSE}
library(tidyverse)
library(rprojroot)
library(knitr)
```

<!-- # Load fake data -->

```{r, include=FALSE}
wcc_df_raw <- readr::read_csv(
  rprojroot::find_rstudio_root_file(
    "data", "raw_ignored", "WCC19_altered.csv"
  )
  , col_types = NULL
  , skip = 0
)

# wcc_df %>% head()
```

<!-- ## Cleaning raw data -->

```{r}
wcc_df <- wcc_df_raw
colnames(wcc_df) <- wcc_df_raw[1,]
wcc_df <- wcc_df[-1,]
```


<!-- ### Filter some of the bad rows -->

```{r}
## filter out the non-agrees
wcc_df <- wcc_df[wcc_df$`By clicking AGREE, you are stating that you (or a child or someone needing help) are currently sick, 18 years or over, and agreeing to share symptom information.` == "Agree", ]
```

<!-- ### create easier variables -->

```{r}
wcc_df$ZIP <- wcc_df$`What is [Field-surveytaker2] ZIP code?`
wcc_df$gender <- wcc_df$`What is [Field-surveytaker2] gender?`
wcc_df$days_sick <- wcc_df$`For how many days have [Field-surveytaker] been sick?`
wcc_df$testing_situation <- wcc_df$`Which best fits [Field-surveytaker2] situation about testing for coronavirus (SARS-CoV-2)?`


wcc_df <- wcc_df %>% 
  mutate(
    days_sick_interval = case_when(
      (days_sick %in% c("1 day", "2 days", "3 days", "4 days")) ~ "sick for 1-4 days"
      ,  (days_sick %in% c("5 days", "6 days", "7 or more days")) ~ "sick for 5+ days"
      , TRUE ~ NA_character_
    )
  )
```


## Initial data views

- This data has `r wcc_df %>% NROW()` rows and `r wcc_df %>% NCOL()` columns. 

```{r}
# wcc_df %>% head()
```


### Zip codes

This is a subset of the total data; it is very long-tailed.

```{r}

wcc_df %>% 
  group_by(ZIP) %>% tally() %>% 
  mutate(number_reporting_illness = ifelse(n > 4, as.character(n),"<= 4")) %>% 
  # filter(n> 2) %>% 
  arrange(desc(n)) %>%
  select(-n) %>%
  head(8) %>% 
  knitr::kable()
```


### Gender

```{r}
wcc_df %>% 
  group_by(gender) %>% tally() %>% 
  arrange(desc(n)) %>% knitr::kable()
```

### Duration of illness
 
Duration of illness at time of survey response. This does not yet adjust for the timestamp on the response. 

```{r}
wcc_df %>% 
  group_by(days_sick) %>% tally() %>% 
  mutate(number_respondents = ifelse(n > 4, as.character(n),"<= 4")) %>% 
  arrange(desc(days_sick)) %>%
  select(-n) %>%
  knitr::kable()
```


### COVID-19 testing status / situation
 
Respondant's COVID-19 test status at time of the survey response, for those who reported being sick.

```{r}
wcc_df %>% 
  filter(!is.na(days_sick)) %>% 
  group_by(testing_situation) %>%
  tally() %>% 
  mutate(number_respondents = ifelse(n > 4, as.character(n),"<= 4")) %>% 
  arrange(desc(n)) %>%
  select(-n) %>%
  knitr::kable()
```


```{r, fig.width= 10}
# wcc_df$`By clicking AGREE, you are stating that you (or a child or someone needing help) are currently sick, 18 years or over, and agreeing to share symptom information.`

wcc_df %>% 
  filter(
    !is.na(days_sick)
    , !is.na(testing_situation)
    , !(testing_situation %in% c(
        "Other","Tested and WAITING for results",
        "Tested and NEGATIVE","Tested and POSITIVE"
    ))
  ) %>% 
  ggplot(
    aes(
      x = testing_situation
      , fill = testing_situation
    )
  ) + 
  geom_bar(stat = "count") + 
  scale_fill_discrete() + 
  theme_bw() + 
  # coord_flip() + 
  theme(
    axis.text.x = element_blank()
    , legend.position = "bottom"
  ) 
  
```



```{r, fig.width= 10}
# wcc_df$`By clicking AGREE, you are stating that you (or a child or someone needing help) are currently sick, 18 years or over, and agreeing to share symptom information.`
# 
# ### Test status by days sick
# wcc_df %>% 
#   filter(
#     !is.na(days_sick)
#     , !is.na(testing_situation)
#     , testing_situation != "Other"
#   ) %>% 
#   ggplot(
#     aes(
#       x = testing_situation
#       , fill = testing_situation
#     )
#   ) + 
#   geom_bar(stat = "count") + 
#   scale_fill_discrete() + 
#   theme_bw() + 
#   # coord_flip() + 
#   theme(
#     axis.text.x = element_blank()
#     , legend.position = "bottom"
#   ) + 
#   facet_grid(
#     days_sick_interval~.
#     , scales = "free_y"
#   )
#   
```



